---
title: "Porf-4"
author: "Heather Hawkins"
date: "2023-04-04"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
 library(tidyverse) 
library(ggeasy) 
library(dsbox) 
library(ggplot2)
library(skimr)
library(haven)
```

Debbie had students take a survey on color and emotion. The survey asked students to rate a color on a scale of 1-6 based on what that color reminds you of a certain emotion. The EMOTIONS were: anger, envy, fear, and jealousy. The colors were "black","green","red","violet","blue","white","pink","yellow", "brown","gray","orange", and "purple". 

I was asked to analyze this data. As it was taken by paper, I had to manually fill in data. 

I was also asked to present this data, so I made graphs for each emotion. 

## Adding DATA


```{r Students_data}

ANGER_debbie <- tribble(
  ~color, ~scale,
  "black", 5,
  "green", 1,
  "red", 6,
  "violet", 2, 
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 4,
  "orange", 4,
  "purple", 5,
  "black", 4,
  "green", 1,
  "red", 6,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow",1,
  "brown", 1,
  "gray", 1,
  "orange", 2,
  "purple", 1,
    "black", 4,
  "green", 1,
  "red", 6,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 3,
  "green", 1,
  "red", 6, 
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 3,
  "green", 1,
  "red", 6,
  "violet", 1,
  "blue", 2,
  "white", 1, 
  "pink", 2,
  "yellow", 2,
  "brown", 4,
  "gray", 3,
  "orange", 5,
  "purple", 1,
    "black", 5,
  "green", 5,
  "red", 6,
  "violet", 1,
  "blue", 1, 
  "white", 6,
  "pink", 3,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 5,
  "purple", 5,
    "black", 6,
  "green", 2,
  "red", 6,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 3,
  "orange", 3,
  "purple", 2,
    "black", 4,
  "green", 2,
  "red", 6,
  "violet", 1,
  "blue", 2,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 4,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 3,
  "red", 6,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 4,
  "green", 2,
  "red", 6,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 3,
  "orange", 2,
  "purple", 1,
    "black", 4,
  "green", 2,
  "red", 6,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 3,
  "gray", 1,
  "orange", 2,
  "purple", 1,
    "black", 4,
  "green", 1,
  "red", 6,
  "violet", 1, 
  "blue", 1, 
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 3,
  "purple", 1,
    "black", 4,
  "green", 1,
  "red", 6,
  "violet", 3,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 4,
  "orange", 2,
  "purple", 1,
    "black", 5,
  "green", 2,
  "red", 6,
  "violet", 2,
  "blue", 1,
  "white", 5,
  "pink", 2,
  "yellow", 1,
  "brown", 1,
  "gray", 2,
  "orange", 3,
  "purple", 2,
    "black", 4,
  "green", 1,
  "red", 6,
  "violet", 3,
  "blue", 2,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 3,
  "orange", 3,
  "purple", 2,
    "black", 4,
  "green", 1,
  "red", 6,
  "violet", 3,
  "blue", 2,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 3,
  "orange", 3,
  "purple", 2,
    "black", 5,
  "green", 1,
  "red", 6,
  "violet", 1,
  "blue", 1,
  "white", 2,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 5, 
  "green", 2,
  "red", 5,
  "violet", 3,
  "blue", 2,
  "white", 2,
  "pink", 2,
  "yellow", 3,
  "brown", 3, 
  "gray", 4,
  "orange", 2,
  "purple", 2,
    "black", 4,
  "green", 2,
  "red", 5,
  "violet", 2,
  "blue", 3,
  "white", 1,
  "pink", 1,
  "yellow", 2,
  "brown", 4,
  "gray", 3,
  "orange", 3,
  "purple", 1,
    "black", 4,
  "green", 1,
  "red", 6,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 2,
  "yellow", 3,
  "brown", 2,
  "gray", 2,
  "orange", 4,
  "purple", 1,
    "black", 5,
  "green", 1,
  "red", 6,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 2,
  "yellow", 1,
  "brown", 1,
  "gray", 2,
  "orange", 5,
  "purple", 1,
    "black", 3,
  "green", 1,
  "red", 6,
  "violet", 3,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 4,
  "green", 3,
  "red", 6,
  "violet", 1,
  "blue", 2,
  "white", 1,
  "pink", 1,
  "yellow", 4,
  "brown", 1,
  "gray", 1,
  "orange", 5,
  "purple", 1,
    "black", 4,
  "green", 1,
  "red", 6,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1
)

##ENVY
ENVY_debbie <- tribble(
  ~color, ~scale,
  "black", 4,
  "green", 5,
  "red", 2,
  "violet", 4,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1, 
  "brown", 1,
  "gray", 2,
  "orange", 1,
  "purple", 5,
    "black", 3,
  "green", 6,
  "red", 3,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 6,
  "red", 4,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 3,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 1,
  "green", 6,
  "red", 1,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 3,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 4,
  "green", 6,
  "red", 1,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 4,
  "brown", 1,
  "gray", 1,
  "orange", 4,
  "purple", 1,
    "black", 3,
  "green", 1,
  "red", 5,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 2,
  "yellow", 3,
  "brown", 2,
  "gray", 3,
  "orange", 5,
  "purple", 1,
    "black", 4,
  "green", 6,
  "red", 5,
  "violet", 3,
  "blue", 2,
  "white", 2,
  "pink", 3,
  "yellow", 4,
  "brown", 3,
  "gray", 4,
  "orange", 3,
  "purple", 3,
    "black", 5,
  "green", 5,
  "red", 5,
  "violet", 3,
  "blue", 2, 
  "white", 2,
  "pink", 2,
  "yellow", 2,
  "brown", 2,
  "gray", 2,
  "orange", 2,
  "purple", 3,
    "black", 4,
  "green", 5,
  "red", 3,
  "violet", 1,
  "blue", 1,
  "white", 2,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 4,
  "green", 3,
  "red", 5,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 3,
  "purple", 3,
    "black", 4,
  "green", 6,
  "red", 4, 
  "violet", 3,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 3,
    "black", 1,
  "green", 5,
  "red", 2,
  "violet", 4,
  "blue", 1,
  "white", 1,
  "pink", 3,
  "yellow", 4,
  "brown", 2,
  "gray", 1,
  "orange", 4,
  "purple", 4,
    "black", 3,
  "green", 2,
  "red", 1,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 4,
  "yellow", 4,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 3,
    "black", 1,
  "green", 6,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 3,
  "gray", 3,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 6,
  "red", 5,
  "violet", 4,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 2,
  "orange", 2, 
  "purple", 4,
    "black", 5,
  "green", 2,
  "red", 4,
  "violet", 5,
  "blue", 3,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 6,
  "red", 5,
  "violet", 1,
  "blue", 1,
  "white", 2,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 3,
  "orange", 1,
  "purple", 3,
    "black", 5,
  "green", 6,
  "red", 6,
  "violet", 4,
  "blue", 3,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 3,
  "gray", 2,
  "orange", 3,
  "purple", 2,
    "black", 5,
  "green", 6,
  "red", 2,
  "violet", 2,
  "blue", 5,
  "white", 2,
  "pink", 2,
  "yellow", 2,
  "brown", 2,
  "gray", 5,
  "orange", 2,
  "purple", 2,
    "black", 3,
  "green", 6,
  "red", 2,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 2,
  "orange", 3,
  "purple", 1,
    "black", 2,
  "green", 6,
  "red", 2,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 1,
  "green", 2,
  "red", 2,
  "violet", 5,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 5,
    "black", 3,
  "green", 6,
  "red", 2,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1
)

##FEAR
FEAR_debbie <- tribble(
  ~color, ~scale,
  "black", 4,
  "green", 2,
  "red", 3,
  "violet", 3,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown",1,
  "gray", 2,
  "orange", 1,
  "purple", 3,
  "black", 4,
"green", 1,
  "red", 4,
  "violet", 1,
  "blue", 5,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 4,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 2,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 6,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 2,
  "green", 2,
  "red", 3,
  "violet", 3,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 2,
  "orange", 1,
  "purple", 1,
    "black", 6,
  "green", 1,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 3,
  "pink", 1,
  "yellow", 6,
  "brown", 1,
  "gray", 4,
  "orange", 3,
  "purple", 1,
    "black", 4,
  "green", 1,
  "red", 3,
  "violet", 2,
  "blue", 2,
  "white", 1,
  "pink", 1, 
  "yellow", 1,
  "brown", 2,
  "gray", 3,
  "orange", 3,
  "purple", 1,
    "black", 5,
  "green", 4,
  "red", 5,
  "violet", 2,
  "blue", 3,
  "white", 3,
  "pink", 1,
  "yellow", 2,
  "brown", 4,
  "gray", 5,
  "orange", 2,
  "purple", 2,
    "black", 5,
  "green", 5,
  "red", 2,
  "violet", 2,
  "blue", 4,
  "white", 2,
  "pink", 2,
  "yellow", 2,
  "brown", 4,
  "gray", 4,
  "orange", 2,
  "purple", 4,
    "black", 5,
  "green", 1,
  "red", 1,
  "violet", 3,
  "blue", 3,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 2,
  "purple", 1,
    "black", 5,
  "green", 1,
  "red", 5,
  "violet", 1,
  "blue", 1,
  "white", 1, 
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 3,
  "orange", 2,
  "purple", 4,
    "black", 6,
  "green", 1,
  "red", 1,
  "violet", 2,
  "blue", 4,
  "white", 3,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 5,
  "orange", 1,
  "purple", 1,
    "black", 6,
  "green", 1,
  "red", 2,
  "violet", 1,
  "blue", 1,
  "white", 3,
  "pink", 1,
  "yellow", 1,
  "brown", 4,
  "gray", 6,
  "orange", 1,
  "purple", 1,
    "black", 4,
  "green", 1,
  "red", 3,
  "violet", 1,
  "blue", 1,
  "white", 3,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 2,
  "red", 3,
  "violet", 1,
  "blue", 3,
  "white", 3,
  "pink", 1,
  "yellow", 1,
  "brown", 4,
  "gray", 4,
  "orange", 1,
  "purple", 1,
    "black", 3,
  "green", 4,
  "red", 2,
  "violet", 2,
  "blue", 4,
  "white", 3,
  "pink", 4,
  "yellow", 1,
  "brown", 2,
  "gray", 5,
  "orange", 2,
  "purple", 1,
    "black", 5,
  "green", 2,
  "red", 1,
  "violet", 1,
  "blue", 3,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 2,
  "orange", 1,
  "purple", 1,
    "black", 6,
  "green", 2,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 5,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 4,
  "orange", 1,
  "purple", 1,
    "black", 2,
  "green", 4,
  "red", 3,
  "violet", 2,
  "blue", 5,
  "white", 6,
  "pink", 2,
  "yellow", 1,
  "brown", 3,
  "gray", 3,
  "orange", 2,
  "purple", 2,
    "black", 6,
  "green", 1,
  "red", 1,
  "violet", 6,
  "blue", 6,
  "white", 2,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 5,
    "black", 1,
  "green", 2,
  "red", 5,
  "violet", 3,
  "blue", 5,
  "white", 1,
  "pink", 2,
  "yellow", 4,
  "brown", 2,
  "gray", 1,
  "orange", 1,
  "purple", 4,
    "black", 5,
  "green", 1,
  "red", 2,
  "violet", 1, 
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 1,
  "red", 3,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 1,
  "red", 3,
  "violet", 1,
  "blue", 4,
  "white", 1, 
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1
)


##JEALOUSY
JEALOUSY_debbie <- tribble(
  ~color, ~scale,
  "black", 4,
  "green", 4,
  "red", 3,
  "violet", 3,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 1,
  "orange", 1,
  "purple", 3,
    "black", 1,
  "green", 6,
  "red", 1,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 4,
    "black", 3,
  "green", 1,
  "red", 5,
  "violet", 1,
  "blue", 2,
  "white", 1, 
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 2,
  "purple", 2,
    "black", 1,
  "green", 1,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 4,
  "green", 3,
  "red", 2,
  "violet", 1,
  "blue", 2,
  "white", 5,
  "pink", 4, 
  "yellow", 4,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 2,
    "black", 5,
  "green", 6,
  "red", 5,
  "violet", 3,
  "blue", 2,
  "white", 2,
  "pink", 2,
  "yellow", 2,
  "brown", 2,
  "gray", 2,
  "orange", 2,
  "purple", 5,
    "black", 6,
  "green", 6,
  "red", 6,
  "violet", 6, 
  "blue", 4,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 2,
  "orange", 5,
  "purple", 6,
    "black", 6,
  "green", 1,
  "red", 6,
  "violet", 1,
  "blue", 1,
  "white", 3,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 3,
  "orange", 1,
  "purple", 1,
    "black", 3,
  "green", 2,
  "red", 2,
  "violet", 1,
  "blue", 2,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 2,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 6,
  "red", 4, 
  "violet", 4, 
  "blue", 3,
  "white", 2,
  "pink", 2,
  "yellow", 1,
  "brown", 1,
  "gray", 3,
  "orange", 2,
  "purple", 3,
    "black", 5,
  "green", 6,
  "red", 4, 
  "violet", 4,
  "blue", 3,
  "white", 2,
  "pink", 2,
  "yellow", 1,
  "brown", 1,
  "gray", 3,
  "orange", 2,
  "purple", 3,
    "black", 3,
  "green", 6,
  "red", 2,
  "violet", 2,
  "blue", 1, 
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 3,
  "gray", 3,
  "orange", 1,
  "purple", 1,
    "black", 1,
  "green", 2,
  "red", 1,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 3,
  "yellow", 3,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 1,
  "green", 5,
  "red", 1,
  "violet",1,
  "blue", 2,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 4,
  "green", 6,
  "red", 5,
  "violet", 4,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 2,
  "brown", 2,
  "gray", 1,
  "orange", 2,
  "purple", 3,
    "black", 4,
  "green", 4, 
  "red", 5,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 2,
  "orange", 2,
  "purple", 3,
    "black", 4,
  "green", 1,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 5,
  "green", 4,
  "red", 5,
  "violet", 4,
  "blue", 2, 
  "white", 2,
  "pink", 2,
  "yellow", 2,
  "brown", 2,
  "gray", 2,
  "orange", 3,
  "purple", 3,
    "black",5,
  "green", 5,
  "red", 5,
  "violet", 2,
  "blue", 4,
  "white", 3,
  "pink", 3,
  "yellow", 2,
  "brown", 3,
  "gray", 5,
  "orange", 4,
  "purple", 2, 
    "black", 4,
  "green", 1,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 2,
  "gray", 3,
  "orange", 3,
  "purple", 1,
    "black", 3,
  "green", 5,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 3,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 4,
  "purple", 1,
    "black", 1,
  "green", 3,
  "red", 2,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1, 
  "gray", 1,
  "orange", 1,
  "purple", 1,
    "black", 4,
  "green", 6,
  "red", 4,
  "violet", 2,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 1,
  "brown", 1,
  "gray", 1,
  "orange", 2,
  "purple", 1,
    "black", 4,
  "green", 4,
  "red", 4,
  "violet", 1,
  "blue", 1,
  "white", 1,
  "pink", 1,
  "yellow", 4,
  "brown", 1,
  "gray", 1,
  "orange", 1,
  "purple", 1
)
```

## Plotting data

This is the average of certain colors for each emotion. 

```{R ANGER}

ANGER_debbie %>%
  group_by(color) %>% 
  summarize(m = mean(scale))

ANGER_debbie %>%
  ggplot(aes(x = color, y = scale, fill= color)) +
  geom_bar(position = "dodge", stat = "summary", fun = "mean") + scale_fill_manual(values = c("black","blue","brown","gray","green","orange","pink","purple", "red","violet","white","yellow")) + labs (x= "Color", Y= "Scale", title = "Representation of ANGER")
```

```{R PLOT_ENVY}
ENVY_debbie %>%
  group_by(color) %>% 
  summarize(m = mean(scale))

ENVY_debbie %>%
  ggplot(aes(x = color, y = scale, fill= color)) +
  geom_bar(position = "dodge", stat = "summary", fun = "mean") + scale_fill_manual(values = c("black","blue","brown","gray","green","orange","pink","purple", "red","violet","white","yellow")) + labs (x= "Color", Y= "Scale", title = "Representation of ENVY")
```

```{R PLOT_FEAR}

FEAR_debbie %>%
  group_by(color) %>% 
  summarize(m = mean(scale))

FEAR_debbie %>%
  ggplot(aes(x = color, y = scale, fill= color)) +
  geom_bar(position = "dodge", stat = "summary", fun = "mean") + scale_fill_manual(values = c("black","blue","brown","gray","green","orange","pink","purple", "red","violet","white","yellow")) + labs (x= "Color", Y= "Scale", title = "Representation of FEAR")
```

```{R PLOT_JEALOUSY}
JEALOUSY_debbie %>%
  group_by(color) %>% 
  summarize(m = mean(scale))

JEALOUSY_debbie %>%
  ggplot(aes(x = color, y = scale, fill= color)) +
  geom_bar(position = "dodge", stat = "summary", fun = "mean") + scale_fill_manual(values = c("black","blue","brown","gray","green","orange","pink","purple", "red","violet","white","yellow")) + labs (x= "Color", Y= "Scale", title = "Representation of JEALOUSY")
```

GENDER PREFER
