---
title: "Thesis Stuff"
author: "Heather Hawkins"
date: "2023-05-15"
output:
  pdf_document: default
  html_document: default
---

```{r load-packages, message = FALSE}
library(rvest)
library(skimr)
library(glue)
library(tidyverse) 
library(usethis)
library(stringi)
library(robotstxt)
```

# Lets filter some data!!

For my thesis, I'm interested in counterfactuals and moral thinking.
This study was basic, as I only asked students to either come up with a counterfactual after thinking about a negative event, or not! The counterfactual were split between upward and downward counterfactuals.

This is RAW data so lets clean it up! 

```{r load}
library(haven)
Personal_Experiences_Assessment_Study_May_15_2023_19_29 <- read_sav("~/Documents/GitHub/Project-1/Porfolio 10/Personal+Experiences+Assessment+Study_May+15,+2023_19.29.sav")
View(Personal_Experiences_Assessment_Study_May_15_2023_19_29)
```
First, lets delete some columns that are unneeded

```{r del}
Thesis_Data <- Personal_Experiences_Assessment_Study_May_15_2023_19_29

Thesis_Data = subset(Thesis_Data, select = -c(StartDate, EndDate, Status, IPAddress, Progress, Finished, Duration__in_seconds_, RecordedDate, ResponseId, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, DistributionChannel, UserLanguage, AgreeParticipate, WTT_First_Click, WTT_Last_Click, WTT_Page_Submit, WTT_Click_Count, id) )

```

Now we need to add the number of counterfactuals for each condition

```{r add}
UP_Coun_Num = c(0, 0, 5, 0, 5, 0, 0, 5, 0, 0, 0, 2, 0, 4, 0, 0, 3, 0, 0, 2, 0, 0, 0, 2, 0, 0, 0, 0, 3, 0, 0, 3, 0, 2, 0, 0, 0, 1, 0, 0, 0, 0, 0, 5, 0, 0, 0, 2, 0, 5, 0, 1, 0, 0, 0, 2, 0, 0, 2, 0, 0, 0, 1, 0, 0, 0, 5, 3, 0, 5, 0, 0, 0, 1, 0, 0, 0, 1, 0, 0, 5, 0, 0, 1, 2, 0, 0, 0, 2, 0, 0, 3, 0, 0, 2, 0, 0)

DOWN_Coun_Num = c(0, 0, 0, 4, 0, 0, 0, 0, 2, 0, 4, 0, 0, 0, 1, 0, 0, 1, 0, 0, 0, 0, 1, 0, 0, 2, 0, 5, 0, 2, 0, 0, 5, 0, 0, 0, 0, 0, 2, 5, 0, 0, 0, 0, 2, 5, 0, 0, 2, 0, 0, 0, 0, 0, 4, 0, 0, 3, 0, 2, 0, 2, 0, 0, 3, 2, 0, 0, 0, 0, 1, 0, 0, 0, 0, 2, 0, 0, 2, 0, 0, 2, 0, 0, 0, 1, 0, 0, 0, 2, 0, 0, 5, 0, 0, 5, 0)

#adding to data frame 

Thesis_Data <- data.frame(Thesis_Data, UP_Coun_Num, DOWN_Coun_Num) 

# Now we need to set the individuals that are not in that condition as 0

Thesis_Data <- Thesis_Data %>% mutate(FL_18_DO_UP_CTP = ifelse(is.na(FL_18_DO_UP_CTP), 0, FL_18_DO_UP_CTP))

Thesis_Data <- Thesis_Data %>% mutate(FL_18_DO_DW_CFTP = ifelse(is.na(FL_18_DO_DW_CFTP), 0, FL_18_DO_DW_CFTP))

Thesis_Data <- Thesis_Data %>% mutate(FL_18_DO_WT = ifelse(is.na(FL_18_DO_WT), 0, FL_18_DO_WT))


# Rename these

colnames(Thesis_Data)[colnames(Thesis_Data) == "FL_18_DO_DW_CFTP"] ="Downward_Participants"

colnames(Thesis_Data)[colnames(Thesis_Data) == "FL_18_DO_UP_CTP"] ="Upward_Participants"

colnames(Thesis_Data)[colnames(Thesis_Data) == "FL_18_DO_WT"] ="Control_Participants"


# Recode and Merge

Thesis_Data$Participants[Thesis_Data$Upward_Participants=="1"] <- "1"
Thesis_Data$Participants[Thesis_Data$Downward_Participants=="1"] <- "2"
Thesis_Data$Participants[Thesis_Data$Control_Participants=="1"] <- "3"


#Now we need to add for the number of Counterfactuals

Thesis_Data <- Thesis_Data %>% mutate(Count_Num = UP_Coun_Num + DOWN_Coun_Num)

#Need to Multiply for CP

Thesis_Data <- Thesis_Data %>% mutate(CF_1 = CTR_IF1 * CTR_TH1)

Thesis_Data <- Thesis_Data %>% mutate(CF_2 = CTR_IF2 * CTR_TH2)

Thesis_Data <- Thesis_Data %>% mutate(CF_3 = CTR_IF3 * CTR_TH3)

Thesis_Data <- Thesis_Data %>% mutate(CF_4 = CTR_IF4 * CTR_TH4)

Thesis_Data <- Thesis_Data %>% mutate(CF_5 = CRT_IF5 * CTR_TH5)

#Divide for Total

Thesis_Data <- Thesis_Data %>% mutate(CF_1_Tot = CF_1 / Count_Num)

Thesis_Data <- Thesis_Data %>% mutate(CF_2_Tot = CF_2 / Count_Num)

Thesis_Data <- Thesis_Data %>% mutate(CF_3_Tot = CF_3 / Count_Num)

Thesis_Data <- Thesis_Data %>% mutate(CF_4_Tot = CF_4 / Count_Num)

Thesis_Data <- Thesis_Data %>% mutate(CF_5_Tot = CF_5 / Count_Num)

#Add All

Thesis_Data <- Thesis_Data %>% mutate(CF_Tot = CF_5 + CF_4 + CF_3 + CF_4 + CF_5)

Thesis_Data <- Thesis_Data %>% mutate(CF_Tot_All = CF_Tot / 5)

# Affect Total

Thesis_Data <- Thesis_Data %>% mutate(Postitive_Affect = PANAS_1 + PANAS_3 + PANAS_5 + PANAS_9 + PANAS_10 + PANAS_12 + PANAS_14 + PANAS_16 + PANAS_17 + PANAS_19)

Thesis_Data <- Thesis_Data %>% mutate(Negative_Affect = PANAS_2 + PANAS_4 + PANAS_6 + PANAS_7 + PANAS_8 + PANAS_11 + PANAS_13 + PANAS_15 + PANAS_18 + PANAS_20)

```

Now, Lets view some data. 

```{r testing}

mean(Thesis_Data$CF_Tot_All, na.rm = T)
mean_culp_all <- mean(Thesis_Data$CF_Tot_All)
mean_culp_all

```

Mean CP is 32.14- meaning that CP is fairly normal overall (0-60 range)


```{r testing6}

mean(Thesis_Data$Postitive_Affect, na.rm = T)
mean_pos_Affect <- mean(Thesis_Data$Postitive_Affect)
mean_pos_Affect

```


```{r testing3}

mean(Thesis_Data$Negative_Affect, na.rm = T)
mean_neg_Affect <- mean(Thesis_Data$Negative_Affect)
mean_neg_Affect

```

Postitive affect overall is higher than negative affect, which is good :)

Now lets compare CP to Positive Affect and Negative Affect for each condition


```{r testing9}
Thesis_Data %>%
  ggplot(Thesis_Data, mapping = aes(x = CF_Tot_All, y= Postitive_Affect, color= Participants))+ geom_point() +labs (x= "Counterfactual Potency", y= "Positive Affect")+labs(color="Type of Participant")+ labs(title= "Affect of Counterfactuals on Positive Affect")+ scale_color_discrete(name = "Type of Participant", labels = c("Upward", "Downward", "Control"))

```

It seems as if those with higher positive affect had lower CP scores, meaning that those who felt alright about the situation afterwards believed their own counterfactuals less. 

```{r testing4}
Thesis_Data %>%
  ggplot(Thesis_Data, mapping = aes(x = CF_Tot_All, y= Negative_Affect, color= Participants))+ geom_point() +labs (x= "Counterfactual Potency", y= "Negative Affect")+labs(color="Type of Participant")+ labs(title= "Affect of Counterfactuals on Negative Affect")+ scale_color_discrete(name = "Type of Participant", labels = c("Upward", "Downward", "Control"))

```

The affect seems to have shift just a liiitttllleee bit here. It seems fairly average on both sides. Average NEgative Affect= Average CP. 

I believe this has helped me look at my data a little bit (especially after the clean up)! 