---
title: "Thesis Stuff P.2"
author: "Heather Hawkins"
date: "2023-04-30"
output:
  html_document: default
---

Let's do some testing with the Thesis Data!!

```{r load-packages, message = FALSE}
library(rvest)
library(skimr)
library(glue)
library(tidyverse) 
library(usethis)
library(stringi)
library(robotstxt)
library(broom)
library(openintro)
library(usethis)
library(stringi)
library(robotstxt)
library(dplyr)
library(stringr)
library(ggplot2)
library(scales)
library(tidyr)
library(dsbox) 
library(haven)
```

Loading 1st :)

```{r }
library(readxl)
Porfolio_10_Thesis_Data <- read_excel("~/Documents/GitHub/Project-1/Porfolio 10/Porfolio 10:Thesis Data.xls")
View(Porfolio_10_Thesis_Data)

Thesis_Data <- Porfolio_10_Thesis_Data
```

Lets start with a linear regression on Counterfactual Potency predicting Affect

```{r n}

Thesis_Data <- Thesis_Data %>% mutate(Postitive_Affect = ifelse(is.na(Postitive_Affect), 0, Postitive_Affect))

Thesis_Data <- Thesis_Data %>% mutate(Negative_Affect = ifelse(is.na(Negative_Affect), 0, Negative_Affect))

                               
Thesis_Data[is.na(Thesis_Data) | Thesis_Data == "Inf"] = NA

M_CP <- lm(CF_Tot_All ~ Postitive_Affect, data = Thesis_Data)
summary(M_CP) 

M_CP <- lm(CF_Tot_All ~ Negative_Affect, data = Thesis_Data)
summary(M_CP)

```

For Positive Affect:

y = 23.80 + 0.301(Pos_aff)

The r\^2 is 0.016 and the adjusted r\^2 is -0.017

This means that for every unit increase in Positive Affect, there is a 0.301 increase in CP

(meaning that those who feel better are better affected by counterfactuals)

For Negative Affect:

y = 32.67 + -0.118(neg_aff)

The r\^2 is 0.025 and the adjusted r\^2 is -0.031

This means that for every unit increase in Negative Affect, there is a -0.118 decrease in CP

(meaning that those who feel worse are less affected by counterfactuals)

## Although this regression shows us a trend, they are both non significant :(

Let's try a multiple regression on these factors!!!

```{r multi}
M_CP <- lm(CF_Tot_All ~ Postitive_Affect + Negative_Affect, data = Thesis_Data)
summary(M_CP)
```

I didn't expect much of a difference, but oof... the p value is worse. (0.4 for positive and 0.59 for negative)

Anyways, let's evaluate the regression.

y = 26.73 + 0.39(Pos_aff) - 0.25(neg_aff)

The r\^2 is 0.026 and the adjusted r\^2 is -0.041

I mean... the numbers are stronger?? :'(

This equation shows that for every unit increase in Positive Affect, there is a 0.39 increase in CP.

It also shows that for every unit increase in Negative Affect, there is a 0.25 decrease in CP..

The r\^2 shows us that only 2.6% variation in CP can be explained by Positive affect and Negative affect.

## This still isn't alot at all. Especially with the high p value.

Lets Continue with a linear regression on Counterfactual Type predicting Affect

(Remember 1= Upward, 2= Downward, 3= Control)

```{r con}
M_PP <- lm(Postitive_Affect ~ Participants, data = Thesis_Data)
summary(M_CP)


M_PN <- lm(Negative_Affect ~ Participants, data = Thesis_Data)
summary(M_CP)
```

Idk what happened to the first participants...

Still non-sig tho :)

For Positive Affect:

y = 27.3 + 1.57(part2) -1.7(part3)

The r\^2 is 0.023 and the adjusted r\^2 is 0.001

This means that for most Downward Counterfactual Participants, there is a 1.57 increase in Positive Affect. For Control Participants, there is a -1.7 decrease in Positive Affect.

(meaning that Downward Counterfactual Participants feel better than Control Participants)

For Negative Affect:

y = 19.8 + 1.57(part2) + 1.46(part3)

The r\^2 is 0.009 and the adjusted r\^2 is 0.014

This means that for most Downward Counterfactual Participants, there is a 1.6 increase in Negative Affect. For Control Participants, there is a 1.5 increase in Negative Affect.

(meaning that Downward Counterfactual Participants and Control Participants both feel similarly bad)

------------------------------------------------------------------------

#Although we pretty much know the answer, let's hypothesis test.

```{r means}

mean(Thesis_Data$Negative_Affect, na.rm = T)
mean_Neg_Aff_Type <- subset(Thesis_Data, Participants= c("1, 2, 3"))$Negative_Affect
mean_Neg_Aff_Type

mean(Thesis_Data$Postitive_Affect, na.rm = T)
mean_Pos_Aff_Type <- subset(Thesis_Data, Participants= c("1, 2, 3"))$Postitive_Affect
mean_Pos_Aff_Type

obs_diff_mean <- mean(mean_Neg_Aff_Type) - mean(mean_Pos_Aff_Type)
obs_diff_mean

```

H0: mean_neg&pos = mean_neg&pos

H1: mean_neg&pos ≠ mean_neg&pos

I mean.... they are different!

```{r final}
t.test(Thesis_Data$Participants ~ Thesis_Data$Postitive_Affect)

t.test(Thesis_Data$Participants ~ Thesis_Data$Negative_Affect)
```

I have more than 2 levels... so this doesn't work. I'm going to have to learn EVEN MORE in r in order to fully test this!


(Note: EVERYTHING WAS WORKING EARLIER, idk what happened. I could see everything, i mean everything, but now it won't knit! :'(  
Of course this happens on the final one. )
