---
title: "Thesis Stuff"
author: "Heather Hawkins"
date: "2023-05-15"
output: html_document
---

```{r load-packages, message = FALSE}
library(rvest)
library(skimr)
library(glue)
library(tidyverse) 
library(usethis)
library(stringi)
library(robotstxt)
```

# Lets filter some data!!

For my thesis, I'm interested in counterfactuals and moral thinking.
This study was basic, as I only asked students to either come up with a counterfactual after thinking about a negative event, or not! The counterfactual were split between upward and downward counterfactuals.

This is RAW data so lets clean it up! 

```{r load}
library(haven)
Personal_Experiences_Assessment_Study_May_15_2023_19_29 <- read_sav("~/Documents/GitHub/Project-1/Porfolio 10/Personal+Experiences+Assessment+Study_May+15,+2023_19.29.sav")
View(Personal_Experiences_Assessment_Study_May_15_2023_19_29)
```
First, lets delete some columns that are unneeded

```{r del}
Thesis_Data <- Personal_Experiences_Assessment_Study_May_15_2023_19_29

Thesis_Data = subset(Thesis_Data, select = -c(StartDate, EndDate, Status, IPAddress, Progress, Finished, Duration__in_seconds_, RecordedDate, ResponseId, RecipientLastName, RecipientFirstName, RecipientEmail, ExternalReference, LocationLatitude, LocationLongitude, DistributionChannel, UserLanguage, AgreeParticipate, WTT_First_Click, WTT_Last_Click, WTT_Page_Submit, WTT_Click_Count, id) )


```

```

