---
title: "Groups"
author: "Heather Hawkins"
date: "2023-01-31"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(dplyr)
library(knitr)
```

---

Loading Students' names and info into R. 

``` {R start}
library(readxl)
Cross_Cult_Groups <- read_excel("~/Documents/GitHub/Project-1/Cross-Cult Groups.xls")
View(Cross_Cult_Groups)
``` 
## R Markdown Part 1

Seeing if the data works and if everything is there.

``` {R data-}
head(Cross_Cult_Groups, n=30)
``` 
## R Markdown Part 2

Randomizing students by name, setting a seed to keep the randomization that was given. 


```{R Groups}
set.seed(32)
random_G<- Cross_Cult_Groups %>% 
  group_by(Name) %>% 
  summarise(Name, Class, Hometown, Major, Minor) %>% 
  sample_n(30) 

##Labeling into 6 groups

ID <- c("1","1","1","1","1","2","2","2","2","2","3","3","3","3","3","4","4","4","4","4","5","5","5","5","5","6","6","6","6","6")


random_G_Final <- cbind(random_G, ID)


view(random_G_Final)
```

```{r Groups_boxplot}
ggplot(data = random_G_Final, aes(x= ID)) +
  geom_bar()+
         facet_wrap(~Class)+ labs(title = "Testing Randomization of Groups (Through Class Distribution)")+
  theme_bw()+
  labs(x = "Group Number", y = "Number of Students")
```

It seems as if there are 3 Freshman, 14, Sophomores, 8 Juniors, and 6 Seniors.


Group 1 consists of 1 Freshman, 3 Sophomores, 1 Junior, and 0 Seniors.

Group 2 consists of 1 Freshman, 1 Sophomore, 0 Juniors, and 3 Seniors.

Group 3 consists of 1 Freshman, 2 Sophomores, 1 Junior, and 1 Senior.

Group 4 consists of 0 Freshman, 2 Sophomores, 2 Juniors, and 1 Senior.

Group 5 consists of 0 Freshman, 3 Sophomores, 1 Junior, and 1 Senior.

Group 6 consists of 0 Freshman, 2 Sophomores, 3 Junior, and 0 Seniors.

Overall, it seems as if only the Sophomores were evenly distributed. The Juniors and Seniors had enough students for at least one of them to be in each group, but this was not so. Additionally, the 3 Freshman were distributed among the first 3 groups, and not too randomly among all 6. 

In all, the groups did not seem to be evenly distributed by class. 

```{r Random_Major}
ggplot(data = random_G_Final, aes(x= ID)) +
  geom_bar()+
         facet_wrap(~Major)+ labs(title = "Testing Randomization of Groups (Through Major Distribution)")+
  theme_bw()+
  labs(x = "Group Number", y = "Number of Students")
```

Overall, it seems as if (soley) Psych Major students were even distributed among groups. 
Additionally, the Majors with one student were evenly distributed. On the other hand, one Major (Health & Science Exercise) had both of its students in one group. 


If the number of students were more than 30, the normal distribution would be more even. With a random assigment of large groups, I could see this code being used. 