---
title: "MTG list"
author: "Heather Hawkins"
date: "2023-05-15"
output: html_document
---

```{r load-packages, message = FALSE}
library(rvest)
library(skimr)
library(glue)
library(tidyverse) 
library(usethis)
library(robotstxt)
```

Because I love Magic the Gathering and I want to look at the new set, I decided to scrape the tcgplayer page of info to look at cards at a glance. 

```{r setup, include=FALSE}

# First we need to set the url

url <- "https://www.tcgplayer.com/search/magic/phyrexia-all-will-be-one?productLineName=magic&setName=phyrexia-all-will-be-one&view=grid&page=1"

#now make a function for this

scrape_page <- function(url) {

  #Then learn to read the url
  
page <- read_html(url)

# I want to know the title, rarity, and price of each card, so I used Selector Gadget to grab the html.nodes.

titles <- page %>%
  html_nodes(".search-result__title")  %>%
  html_node("") %>%
  html_text() %>% 
  str_squish()

rarity <- page %>%
  html_nodes(".search-result__rarity span:nth-child(1)") %>%
  html_text()

price <- page %>%
  html_nodes(".inventory__price-with-shipping") %>%
  html_text()

#It seemed to have collected it so lets create a tibble

  tibble(title = titles, 
         rarity = rarity,
         price = price)
  
}

# Now lets grab all of the pages in this set

root <- "https://www.tcgplayer.com/search/magic/phyrexia-all-will-be-one?productLineName=magic&setName=phyrexia-all-will-be-one&view=grid&page="
numbers <- seq(from = 1, to = 23, by = 1)
urls <- glue("{root}{numbers}")

#and now make a dataframe
phyrexia_mtg.df <- map_dfr(urls, scrape_page)

write_csv(phyrexia_mtg.df, file = "phyrexia_mtg.csv")

phyrexia_mtg <- read_csv("phyrexia_mtg.csv")

```
...The dataframe is empty. Idk what happened. 
Lets just try a single page. 

```{r onepage}

root <- "https://www.tcgplayer.com/search/magic/phyrexia-all-will-be-one?productLineName=magic&setName=phyrexia-all-will-be-one&view=grid&page="
numbers1 <- seq(from = 1, to = 1, by = 1)
urls1 <- glue("{root}{numbers1}")

#and now make a dataframe
phyrexia_mtg.df.1 <- map_dfr(urls, scrape_page)

write_csv(phyrexia_mtg.df.1, file = "phyrexia_mtg.csv")

phyrexia_mtg <- read_csv("phyrexia_mtg.csv")
```
Im gonna cry idk what happened. Its not grabbing the info.... I assume the website will not let me grab the info, or there is something else wrong. 

Idk :( Ill retry this in another project

