---
title: "P5"
author: "Heather Hawkins"
date: "2023-03-18"
output: html_document
---
So I was looking online for some free datasets with locations to play around with, (Lat and Long), so I can practice the distance functions, and I found SEVERAL datasets based in Washington, DC that were made 6 years ago.


```{r load}
library(dplyr)
library(stringr)
library(ggplot2)
library(scales)
library(tidyr)
library(tidyverse) 
library(dsbox) 
```

Two of these datasets caught my eye, so I wondered if the had any relation. As arbirtary as it sounds, I wondered if there were many places that sold Liquor near Homeless Shelters. 


```{r data}
library(readxl)
Liquor_License_Locations <- read_excel("~/Documents/GitHub/Project-1/Porfolio 5/Liquor License Locations.xlsx")
View(Liquor_License_Locations)

library(readxl)
Homeless_Shelter_Locations <- read_excel("~/Documents/GitHub/Project-1/Porfolio 5/Homeless Shelter Locations.xlsx")
View(Homeless_Shelter_Locations)
```

First, I wanted to visually see this data, so I added a coloum to separate the locations and bound the dataset togeather. 

```{r ok}
Location= c(1)

Hm <- cbind(Homeless_Shelter_Locations, Location)

Location= c(2)

Lq <- cbind(Liquor_License_Locations, Location)

HM_LQ <- full_join(Hm, Lq, by = "Location")

HM_LQ2 <- full_join(Hm, Lq)

ggplot(HM_LQ2, mapping = aes(x = longitude,
                            y = latitude,
                            color = Location)) +
  geom_point()
```
After looking at this plot,
It seems as if there are ALOT of Places that legaly sell Liquor in DC. But not too many shelters. 

Now lets see how many Liquor establishments are close to Homeless Shelters. 

First lets do the equation. 


```{R haversine}
haversine <- function(long1, lat1, long2, lat2, round = 3) {
  
  long1 = long1 * pi / 180
  lat1  = lat1  * pi / 180
  long2 = long2 * pi / 180
  lat2  = lat2  * pi / 180
  
  R = 6371 
  
  a = sin((lat2 - lat1)/2)^2 + cos(lat1) * cos(lat2) * sin((long2 - long1)/2)^2
  d = R * 2 * asin(sqrt(a))
  
  return( round(d,round) ) 
}

HM_LQ$latitude.x <- as.numeric(as.character(HM_LQ$latitude.x))
HM_LQ$longitude.x <- as.numeric(as.character(HM_LQ$longitude.x))
HM_LQ$latitude.y <- as.numeric(as.character(HM_LQ$latitude.y))
HM_LQ$longitude.y <- as.numeric(as.character(HM_LQ$longitude.y))
```

Now lets link them and set the equation. 

```{R Distances}
HM_LQ <- HM_LQ %>% mutate(distance = haversine(longitude.x,latitude.x,longitude.y,latitude.y))
```
...

```{R min-distance}
HM_LQ_mindist <- HM_LQ %>%
  group_by(ADDRESS.x) %>%
  summarize(closest = min(distance))
```
....

Now lets see this happen. 

```{R Final-Distance}
view(HM_LQ_mindist)

HM_LQ_mindist %>%
  ggplot(aes(x=closest))+
  geom_bar()+
  labs(title = "Closest Distance between Homeless Shelter and Places with Liqour Licenses",
       x="Distance in kilometers",
       y="Number of locations")
```

Athough it is blank, this information HAS told us that there are 61 locations that are very close to each other. 

This is most likely due to the number of Liquor establishments (1984) compared to the number of Homeless Shelters (64).

OF COURSE so many liquor stores are near homeless shelters in DC... 
There are so many liqour stores in DC in general!